Model LF

### 2022-12-19 paper version 2.Rmd
Commit

@@

COMMENT> 
BEHAVIORAL> wage_ds
TSRANGE 2006 3 2020 1
EQ> TSDELTALOG(wage_ds) = p_522* TSDELTA(TSLAG(ur,4)) + p_523* TSDELTALOG(prod_ds)  + p_524* LOG(TSLAG(wage_ds,1)) + p_525* LOG(TSLAG(wage_ds_t,1)) + p_526* LOG(TSLAG(prod_ds,1))  + p_527 * (d_2009q1 + d_2009q2)
COEFF> p_522 p_523 p_524 p_525 p_526 p_527
STORE> coe(20)

@@

```{r}
###Gengivelse af stød til model
part_bs1 = Shock_bs1$simulation$part
unemp_bs1 = Shock_bs1$simulation$unemp
komp_r_bs1 = Shock_bs1$simulation$komp_r
part_bs1 = Shock_bs1$simulation$part
yk_ds_bs1 = Shock_bs1$simulation$yk_ds
pc_ds_bs1 = Shock_bs1$simulation$pc_ds
wage_ds_t_bs1 = Shock_bs1$simulation$wage_ds_t
ur_ds_bs1 = Shock_bs1$simulation$ur_ds
emp_bs1 = Shock_bs1$simulation$emp
yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
pconk_ds_bs1= Shock_bs1$simulation$pconk_ds
tilpas_pr_bs1 = Shock_bs1$simulation$tilpas_pr
u_ds_bs1 = Shock_bs1$simulation$u_ds
part_bs1 = Shock_bs1$simulation$part
nben_h_bs1 = Shock_bs1$simulation$nben_h
wage_ds_bs1 = Shock_bs1$simulation$wage_ds
dp_person_bs1 = Shock_bs1$simulation$dp_person
kont_h_ratio_bs1 = Shock_bs1$simulation$kont_h_ratio
unemp_bs1 = Shock_bs1$simulation$unemp
nl_g_bs1 = Shock_bs1$simulation$nl_g
inflation_bs1 = Shock_bs1$simulation$inflation
lf_bs1 = Shock_bs1$simulation$lf
yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
wage_gap1_bs1 = Shock_bs1$simulation$wage_gap1
wage_gap_bs1 = Shock_bs1$simulation$wage_gap
prod_bs1 = Shock_bs1$simulation$prod
prodk_ds_bs1 = Shock_bs1$simulation$prodk_ds
max_dp_bs1 = Shock_bs1$simulation$max_dp
wage_ds_t_bs1 = Shock_bs1$simulation$wage_ds_t
xk_ds_bs1 = Shock_bs1$simulation$xk_ds
mk_ds_bs1 = Shock_bs1$simulation$mk_ds

net_balance_bs1 = xk_ds_bs1 - mk_ds_bs1
net_balance_bs1_ratio= (xk_ds_bs1 - mk_ds_bs1)/yk_ds_bs1

@@

```{r}
###Gengivelse af stød til model
max_dp_bs2 = Shock_bs2$simulation$max_dp
wage_bs2 = Shock_bs2$simulation$wage
komp_r_bs2 = Shock_bs2$simulation$komp_r
part_bs2 = Shock_bs2$simulation$part
yk_ds_bs2 = Shock_bs2$simulation$yk_ds
pc_ds_bs2 = Shock_bs2$simulation$pc_ds
wage_ds_t_bs2 = Shock_bs2$simulation$wage_ds_t
ur_ds_bs2 = Shock_bs2$simulation$ur_ds
emp_bs2 = Shock_bs2$simulation$emp
yd_hk_ds_bs2 = Shock_bs2$simulation$yd_hk_ds
pconk_ds_bs2= Shock_bs2$simulation$pconk_ds
tilpas_pr_bs2 = Shock_bs2$simulation$tilpas_pr
u_ds_bs2 = Shock_bs2$simulation$u_ds
part_bs2 = Shock_bs2$simulation$part
nben_h_bs2 = Shock_bs2$simulation$nben_h
wage_ds_bs2 = Shock_bs2$simulation$wage_ds
dp_person_bs2 = Shock_bs2$simulation$dp_person
kont_h_ratio_bs2 = Shock_bs2$simulation$kont_h_ratio
unemp_bs2 = Shock_bs2$simulation$unemp
nl_g_bs2 = Shock_bs2$simulation$nl_g
inflation_bs2 = Shock_bs2$simulation$inflation
lf_bs2 = Shock_bs2$simulation$lf
yd_hk_ds_bs2 = Shock_bs2$simulation$yd_hk_ds
wage_gap1_bs2 = Shock_bs2$simulation$wage_gap1
wage_gap_bs2 = Shock_bs2$simulation$wage_gap
prod_bs2 = Shock_bs2$simulation$prod
prod_bs2 = Shock_bs2$simulation$prod
ws_bs2 = Shock_bs2$simulation$ws
xk_ds_bs2 = Shock_bs2$simulation$xk_ds
mk_ds_bs2 = Shock_bs2$simulation$mk_ds

@@

```{r}
###Gengivelse af stød til model
max_dp_bs3 = Shock_bs3$simulation$max_dp
wage_bs3 = Shock_bs3$simulation$wage
komp_r_bs3 = Shock_bs3$simulation$komp_r
part_bs3 = Shock_bs3$simulation$part
yk_ds_bs3 = Shock_bs3$simulation$yk_ds
pc_ds_bs3 = Shock_bs3$simulation$pc_ds
wage_ds_t_bs3 = Shock_bs3$simulation$wage_ds_t
ur_ds_bs3 = Shock_bs3$simulation$ur_ds
emp_bs3 = Shock_bs3$simulation$emp
yd_hk_ds_bs3 = Shock_bs3$simulation$yd_hk_ds

@@

shock_wage_ds_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

```{r}
###Gengivelse af stød til model
max_dp_bs4 = Shock_bs4$simulation$max_dp
wage_bs4 = Shock_bs4$simulation$wage
komp_r_bs4 = Shock_bs4$simulation$komp_r
part_bs4 = Shock_bs4$simulation$part
yk_ds_bs4 = Shock_bs4$simulation$yk_ds
pc_ds_bs4 = Shock_bs4$simulation$pc_ds
wage_ds_t_bs4 = Shock_bs4$simulation$wage_ds_t
ur_ds_bs4 = Shock_bs4$simulation$ur_ds
emp_bs4 = Shock_bs4$simulation$emp
yd_hk_ds_bs4 = Shock_bs4$simulation$yd_hk_ds

tilpas_pr_bs4 = Shock_bs4$simulation$tilpas_pr
u_ds_bs4 = Shock_bs4$simulation$u_ds
part_bs4 = Shock_bs4$simulation$part
nben_h_bs4 = Shock_bs4$simulation$nben_h
wage_ds_bs4 = Shock_bs4$simulation$wage_ds
dp_person_bs4 = Shock_bs4$simulation$dp_person
kont_h_ratio_bs4 = Shock_bs4$simulation$kont_h_ratio

@@

```{r}
###Gengivelse af stød til model
max_dp_01 = Shock_1$simulation$max_dp
wage_01 = Shock_1$simulation$wage
komp_r_01 = Shock_1$simulation$komp_r
part_01 = Shock_1$simulation$part
yk_ds_01 = Shock_1$simulation$yk_ds
pc_ds_01 = Shock_1$simulation$pc_ds
wage_ds_t_01 = Shock_1$simulation$wage_ds_t
ur_ds_01 = Shock_1$simulation$ur_ds
emp_01 = Shock_1$simulation$emp
yd_hk_ds_01 = Shock_1$simulation$yd_hk_ds

@@

@@

yk_ds_02 = Shock_2$simulation$yk_ds
emp_02 = Shock_2$simulation$emp
wage_ds_02 = Shock_2$simulation$wage_ds
ur_ds_02 = Shock_2$simulation$ur_ds
pc_ds_02 = Shock_2$simulation$pc_ds
yd_hk_ds_02 = Shock_2$simulation$yd_hk_ds
pconk_ds_02 = Shock_2$simulation$pconk_ds
komp_r_02 = Shock_2$simulation$komp_r
max_dp_02 = Shock_2$simulation$max_dp
nben_h_02 = Shock_2$simulation$nben_h
yd_hk_ds_02 = Shock_2$simulation$yd_hk_ds
ik_02 = Shock_2$simulation$ik
wage_ds_t_02 = Shock_2$simulation$wage_ds_t
nben_h_un_02 = Shock_2$simulation$nben_h_un
nl_g_02 = Shock_2$simulation$nl_g
nsben_h_02 = Shock_2$simulation$nsben_h
dp_person_02 = Shock_2$simulation$dp_person
xk_ds_02 = Shock_2$simulation$xk_ds
mk_ds_02 = Shock_2$simulation$mk_ds
ik_02 = Shock_2$simulation$ik
rer_02 = Shock_2$simulation$rer
ps_ds_02 = Shock_2$simulation$ps_ds
i_bd_nfc_k_ds_02 = Shock_2$simulation$i_bd_nfc_k_ds
yd1_hk_ds_02 = Shock_2$simulation$yd1_hk_ds
yd2a_hk_ds_02 = Shock_2$simulation$yd2a_hk_ds
yd2b_hk_02 = Shock_2$simulation$yd2b_hk
i_equip_nfc_k_ds_02 = Shock_2$simulation$i_equip_nfc_k_ds
u_ds_02 = Shock_2$simulation$u_ds
wage_gap1_02 = Shock_2$simulation$wage_gap1
gk_02 = Shock_2$simulation$gk
kont_h_ratio_02 = Shock_2$simulation$kont_h_ratio
lf_02 = Shock_2$simulation$lf
wage_gap_02 = Shock_2$simulation$wage_gap
max_gap_02 = Shock_2$simulation$max_gap
unemp_02 = Shock_2$simulation$unemp
inflation_02 = Shock_2$simulation$inflation
prod_02 = Shock_2$simulation$prod
ws_02 = Shock_2$simulation$ws
net_balance_02 = xk_ds_02 - mk_ds_02
```

@@

yk_ds_03 = Shock_3$simulation$yk_ds
emp_03 = Shock_3$simulation$emp
wage_ds_03 = Shock_3$simulation$wage_ds
ur_ds_03 = Shock_3$simulation$ur_ds
pc_ds_03 = Shock_3$simulation$pc_ds
yd_hk_ds_03 = Shock_3$simulation$yd_hk_ds
pconk_ds_03 = Shock_3$simulation$pconk_ds
komp_r_03 = Shock_3$simulation$komp_r
max_dp_03 = Shock_3$simulation$max_dp
nben_h_03 = Shock_3$simulation$nben_h
yd_hk_ds_03 = Shock_3$simulation$yd_hk_ds
ik_03 = Shock_3$simulation$ik
wage_ds_t_03 = Shock_3$simulation$wage_ds_t
nben_h_un_03 = Shock_3$simulation$nben_h_un
nl_g_03 = Shock_3$simulation$nl_g
nsben_h_03 = Shock_3$simulation$nsben_h
dp_person_03 = Shock_3$simulation$dp_person
part1_03 = Shock_3$simulation$part1
u_ds_03 = Shock_3$simulation$u_ds
kont_h_ratio_03 = Shock_3$simulation$kont_h_ratio
part_03 = Shock_3$simulation$part
unemp_03 = Shock_3$simulation$unemp
rw_ds_03 = Shock_3$simulation$rw_ds
kuld_03 = Shock_3$simulation$shock_kuld
inflation_03 = Shock_3$simulation$inflation
lf_03 = Shock_3$simulation$lf
prod_03 = Shock_3$simulation$prod
```

```{r}
# Define add-factor list (defining shock)
constantAdjList_4 <- list(
 shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q')
)

@@

@@

plot(((nl_g_01 - nl_g_bs1)), col= "black", xlab= "Year", main= "Government net lending",  ylab= "Change in government net lending");
grid()

plot(((yd_hk_ds_01 - yd_hk_ds_bs1) / yd_hk_ds_bs1)*100, col= "black", xlab= "Year", main= "Households disp. income", ylab= "% Change in households disposable income");
grid()
```

@@

```{r}
plot(((unemp_01 - unemp_bs1)*1000), col= "blue", xlab= "Year", ylab= "Change in unemployment (people)", main= "Unemployment", ylim= c(-300,3000));
lines(((unemp_02 - unemp_bs2)*1000), col= "green");
lines(((unemp_03 - unemp_bs3)*1000 ), col= "red");
legend("left", legend=c("Scenario 1","Scenario 2", "Scenario 3"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue", "green", "red"));
grid()
```

>>>>

IDENTITY> part
EQ> part = lf*1000/pop
IF> shock_lf_model > 0

@@

COMMENT> 
BEHAVIORAL> wage_ds
TSRANGE 2006 3 2020 1
EQ> TSDELTALOG(wage_ds) = p_522* TSDELTA(TSLAG(ur,1)) + p_523* TSDELTALOG(prod_ds)  + p_524* LOG(TSLAG(wage_ds,1)) + p_525* LOG(TSLAG(wage_ds_t,1)) + p_526* LOG(TSLAG(prod_ds,1))  + p_527 * (d_2009q1 + d_2009q2)
COEFF> p_522 p_523 p_524 p_525 p_526 p_527
STORE> coe(20)

@@

```{r}
###Gengivelse af stød til model
part_bs1 = Shock_bs1$simulation$part
unemp_bs1 = Shock_bs1$simulation$unemp
komp_r_bs1 = Shock_bs1$simulation$komp_r
part_bs1 = Shock_bs1$simulation$part
yk_ds_bs1 = Shock_bs1$simulation$yk_ds
pc_ds_bs1 = Shock_bs1$simulation$pc_ds
wage_ds_t_bs1 = Shock_bs1$simulation$wage_ds_t
ur_ds_bs1 = Shock_bs1$simulation$ur_ds
emp_bs1 = Shock_bs1$simulation$emp
yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
pconk_ds_bs1= Shock_bs1$simulation$pconk_ds
tilpas_pr_bs1 = Shock_bs1$simulation$tilpas_pr
u_ds_bs1 = Shock_bs1$simulation$u_ds
part_bs1 = Shock_bs1$simulation$part
nben_h_bs1 = Shock_bs1$simulation$nben_h
wage_ds_bs1 = Shock_bs1$simulation$wage_ds
dp_person_bs1 = Shock_bs1$simulation$dp_person
kont_h_ratio_bs1 = Shock_bs1$simulation$kont_h_ratio
unemp_bs1 = Shock_bs1$simulation$unemp
nl_g_bs1 = Shock_bs1$simulation$nl_g
inflation_bs1 = Shock_bs1$simulation$inflation
lf_bs1 = Shock_bs1$simulation$lf
yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
wage_gap1_bs1 = Shock_bs1$simulation$wage_gap1
wage_gap_bs1 = Shock_bs1$simulation$wage_gap
prod_bs1 = Shock_bs1$simulation$prod
prodk_ds_bs1 = Shock_bs1$simulation$prodk_ds
max_dp_bs1 = Shock_bs1$simulation$max_dp
wage_ds_t_bs1 = Shock_bs1$simulation$wage_ds_t
xk_ds_bs1 = Shock_bs1$simulation$xk_ds
mk_ds_bs1 = Shock_bs1$simulation$mk_ds
lf_bs1 = Shock_bs1$simulation$lf
net_balance_bs1 = xk_ds_bs1 - mk_ds_bs1
net_balance_bs1_ratio= (xk_ds_bs1 - mk_ds_bs1)/yk_ds_bs1
nben_h_un_bs1 = Shock_bs1$simulation$nben_h_un

@@

```{r}
###Gengivelse af stød til model
max_dp_bs2 = Shock_bs2$simulation$max_dp
wage_bs2 = Shock_bs2$simulation$wage
komp_r_bs2 = Shock_bs2$simulation$komp_r
part_bs2 = Shock_bs2$simulation$part
yk_ds_bs2 = Shock_bs2$simulation$yk_ds
pc_ds_bs2 = Shock_bs2$simulation$pc_ds
wage_ds_t_bs2 = Shock_bs2$simulation$wage_ds_t
ur_ds_bs2 = Shock_bs2$simulation$ur_ds
emp_bs2 = Shock_bs2$simulation$emp
yd_hk_ds_bs2 = Shock_bs2$simulation$yd_hk_ds
pconk_ds_bs2= Shock_bs2$simulation$pconk_ds
tilpas_pr_bs2 = Shock_bs2$simulation$tilpas_pr
u_ds_bs2 = Shock_bs2$simulation$u_ds
part_bs2 = Shock_bs2$simulation$part
nben_h_bs2 = Shock_bs2$simulation$nben_h
wage_ds_bs2 = Shock_bs2$simulation$wage_ds
dp_person_bs2 = Shock_bs2$simulation$dp_person
kont_h_ratio_bs2 = Shock_bs2$simulation$kont_h_ratio
unemp_bs2 = Shock_bs2$simulation$unemp
nl_g_bs2 = Shock_bs2$simulation$nl_g
inflation_bs2 = Shock_bs2$simulation$inflation
lf_bs2 = Shock_bs2$simulation$lf
yd_hk_ds_bs2 = Shock_bs2$simulation$yd_hk_ds
wage_gap1_bs2 = Shock_bs2$simulation$wage_gap1
wage_gap_bs2 = Shock_bs2$simulation$wage_gap
prod_bs2 = Shock_bs2$simulation$prod
prod_bs2 = Shock_bs2$simulation$prod
ws_bs2 = Shock_bs2$simulation$ws
xk_ds_bs2 = Shock_bs2$simulation$xk_ds
mk_ds_bs2 = Shock_bs2$simulation$mk_ds
nben_h_un_bs2 = Shock_bs2$simulation$nben_h_un

@@

```{r}
###Gengivelse af stød til model
max_dp_bs3 = Shock_bs3$simulation$max_dp
wage_bs3 = Shock_bs3$simulation$wage
komp_r_bs3 = Shock_bs3$simulation$komp_r
part_bs3 = Shock_bs3$simulation$part
yk_ds_bs3 = Shock_bs3$simulation$yk_ds
pc_ds_bs3 = Shock_bs3$simulation$pc_ds
wage_ds_t_bs3 = Shock_bs3$simulation$wage_ds_t
ur_ds_bs3 = Shock_bs3$simulation$ur_ds
emp_bs3 = Shock_bs3$simulation$emp
yd_hk_ds_bs3 = Shock_bs3$simulation$yd_hk_ds
nben_h_un_bs3 = Shock_bs3$simulation$nben_h_un

@@

shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q')
)

@@

```{r}
###Gengivelse af stød til model
max_dp_bs4 = Shock_bs4$simulation$max_dp
wage_bs4 = Shock_bs4$simulation$wage
komp_r_bs4 = Shock_bs4$simulation$komp_r
part_bs4 = Shock_bs4$simulation$part
yk_ds_bs4 = Shock_bs4$simulation$yk_ds
pc_ds_bs4 = Shock_bs4$simulation$pc_ds
wage_ds_t_bs4 = Shock_bs4$simulation$wage_ds_t
ur_ds_bs4 = Shock_bs4$simulation$ur_ds
emp_bs4 = Shock_bs4$simulation$emp
yd_hk_ds_bs4 = Shock_bs4$simulation$yd_hk_ds
lf_bs4 = Shock_bs4$simulation$lf
tilpas_pr_bs4 = Shock_bs4$simulation$tilpas_pr
u_ds_bs4 = Shock_bs4$simulation$u_ds
part_bs4 = Shock_bs4$simulation$part
nben_h_bs4 = Shock_bs4$simulation$nben_h
wage_ds_bs4 = Shock_bs4$simulation$wage_ds
dp_person_bs4 = Shock_bs4$simulation$dp_person
kont_h_ratio_bs4 = Shock_bs4$simulation$kont_h_ratio

@@

```{r}
###Gengivelse af stød til model
max_dp_01 = Shock_1$simulation$max_dp
wage_01 = Shock_1$simulation$wage
komp_r_01 = Shock_1$simulation$komp_r
part_01 = Shock_1$simulation$part
yk_ds_01 = Shock_1$simulation$yk_ds
pc_ds_01 = Shock_1$simulation$pc_ds
wage_ds_t_01 = Shock_1$simulation$wage_ds_t
ur_ds_01 = Shock_1$simulation$ur_ds
emp_01 = Shock_1$simulation$emp
yd_hk_ds_01 = Shock_1$simulation$yd_hk_ds
nben_h_un_01 = Shock_1$simulation$nben_h_un

@@

```{r}
plot(part_01, col= "red"); lines(part_bs4, col = "blue");
legend("top",legend=c("Baseline", "Data"),lty=c(1,1),lwd=c(2),bty="n", col = c("red", "blue")); 
grid()
```

```{r}
plot(lf_01, col= "red"); lines(lf_bs4, col = "blue");
legend("top",legend=c("Baseline", "Data"),lty=c(1,1),lwd=c(2),bty="n", col = c("red", "blue")); 
grid()

plot(((yk_ds_04 - yk_ds_bs4) / yk_ds_bs4), col= "black", xlab= "Year", ylab= "% Change in gdp");
legend("top", legend=c("GDP"),
       lty=c(1),lwd=c(2),bty="n", col = c("black"));
grid()

plot(((unemp_04 - unemp_bs4) / unemp_bs4), col= "black", xlab= "Year", ylab= "% Change in employment");
legend("top", legend=c("Employment"),
       lty=c(1),lwd=c(2),bty="n", col = c("black"));
grid()
```

```{r}
plot((unemp_04-unemp_bs4)*1000, col= "red");

plot((lf_04-lf_bs4)*1000, col= "red");

plot((emp_04-emp_bs4)*1000, col= "red");
```

@@

nben_h_un_02 = Shock_2$simulation$nben_h_un
yk_ds_02 = Shock_2$simulation$yk_ds
emp_02 = Shock_2$simulation$emp
wage_ds_02 = Shock_2$simulation$wage_ds
ur_ds_02 = Shock_2$simulation$ur_ds
pc_ds_02 = Shock_2$simulation$pc_ds
yd_hk_ds_02 = Shock_2$simulation$yd_hk_ds
pconk_ds_02 = Shock_2$simulation$pconk_ds
komp_r_02 = Shock_2$simulation$komp_r
max_dp_02 = Shock_2$simulation$max_dp
nben_h_02 = Shock_2$simulation$nben_h
yd_hk_ds_02 = Shock_2$simulation$yd_hk_ds
ik_02 = Shock_2$simulation$ik
wage_ds_t_02 = Shock_2$simulation$wage_ds_t
nben_h_un_02 = Shock_2$simulation$nben_h_un
nl_g_02 = Shock_2$simulation$nl_g
nsben_h_02 = Shock_2$simulation$nsben_h
dp_person_02 = Shock_2$simulation$dp_person
xk_ds_02 = Shock_2$simulation$xk_ds
mk_ds_02 = Shock_2$simulation$mk_ds
ik_02 = Shock_2$simulation$ik
rer_02 = Shock_2$simulation$rer
ps_ds_02 = Shock_2$simulation$ps_ds
i_bd_nfc_k_ds_02 = Shock_2$simulation$i_bd_nfc_k_ds
yd1_hk_ds_02 = Shock_2$simulation$yd1_hk_ds
yd2a_hk_ds_02 = Shock_2$simulation$yd2a_hk_ds
yd2b_hk_02 = Shock_2$simulation$yd2b_hk
i_equip_nfc_k_ds_02 = Shock_2$simulation$i_equip_nfc_k_ds
u_ds_02 = Shock_2$simulation$u_ds
wage_gap1_02 = Shock_2$simulation$wage_gap1
gk_02 = Shock_2$simulation$gk
kont_h_ratio_02 = Shock_2$simulation$kont_h_ratio
lf_02 = Shock_2$simulation$lf
wage_gap_02 = Shock_2$simulation$wage_gap
max_gap_02 = Shock_2$simulation$max_gap
unemp_02 = Shock_2$simulation$unemp
inflation_02 = Shock_2$simulation$inflation
prod_02 = Shock_2$simulation$prod
ws_02 = Shock_2$simulation$ws
net_balance_02 = xk_ds_02 - mk_ds_02
```

@@

yk_ds_03 = Shock_3$simulation$yk_ds
emp_03 = Shock_3$simulation$emp
wage_ds_03 = Shock_3$simulation$wage_ds
ur_ds_03 = Shock_3$simulation$ur_ds
pc_ds_03 = Shock_3$simulation$pc_ds
yd_hk_ds_03 = Shock_3$simulation$yd_hk_ds
pconk_ds_03 = Shock_3$simulation$pconk_ds
komp_r_03 = Shock_3$simulation$komp_r
max_dp_03 = Shock_3$simulation$max_dp
nben_h_03 = Shock_3$simulation$nben_h
yd_hk_ds_03 = Shock_3$simulation$yd_hk_ds
ik_03 = Shock_3$simulation$ik
wage_ds_t_03 = Shock_3$simulation$wage_ds_t
nben_h_un_03 = Shock_3$simulation$nben_h_un
nl_g_03 = Shock_3$simulation$nl_g
nsben_h_03 = Shock_3$simulation$nsben_h
dp_person_03 = Shock_3$simulation$dp_person
part1_03 = Shock_3$simulation$part1
u_ds_03 = Shock_3$simulation$u_ds
kont_h_ratio_03 = Shock_3$simulation$kont_h_ratio
part_03 = Shock_3$simulation$part
unemp_03 = Shock_3$simulation$unemp
rw_ds_03 = Shock_3$simulation$rw_ds
kuld_03 = Shock_3$simulation$shock_kuld
inflation_03 = Shock_3$simulation$inflation
lf_03 = Shock_3$simulation$lf
prod_03 = Shock_3$simulation$prod
nben_h_un_03 = Shock_3$simulation$nben_h_un

## Scenario 4

```{r}
# Define add-factor list (defining shock)
constantAdjList_4 <- list(
 shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q')
)

@@

```{r}
plot(part_04, col= "red"); lines(part_bs4, col = "blue");
legend("top",legend=c("Baseline", "Data"),lty=c(1,1),lwd=c(2),bty="n", col = c("red", "blue")); 
grid()
```

```{r}
plot(lf_04, col= "red"); lines(lf_bs4, col = "blue");
legend("top",legend=c("Baseline", "Data"),lty=c(1,1),lwd=c(2),bty="n", col = c("red", "blue")); 
grid()

plot(((yk_ds_04 - yk_ds_bs4) / yk_ds_bs4), col= "black", xlab= "Year", ylab= "% Change in gdp");
legend("top", legend=c("GDP"),
       lty=c(1),lwd=c(2),bty="n", col = c("black"));
grid()

plot(((unemp_04 - unemp_bs4) / unemp_bs4), col= "black", xlab= "Year", ylab= "% Change in employment");
legend("top", legend=c("Employment"),
       lty=c(1),lwd=c(2),bty="n", col = c("black"));
grid()
```

```{r}
plot((unemp_04-unemp_bs4)*1000, col= "red");

plot((lf_04-lf_bs4)*1000, col= "red");

plot((emp_04-emp_bs4)*1000, col= "red");
```

@@

@@

```{r}
plot(((unemp_01 - unemp_bs1)*1000), col= "blue", xlab= "Year", ylab= "Change in unemployment (people)", main= "Unemployment", ylim= c(-300,3000));
lines(((unemp_02 - unemp_bs2)*1000), col= "green");
lines(((unemp_03 - unemp_bs3)*1000 ), col= "red");
legend("left", legend=c("Scenario 1","Scenario 2", "Scenario 3"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue", "green", "red"));
grid()

plot(((nben_h_un_01 - nben_h_un_bs1)*1000), col= "blue", xlab= "Year", ylab= "Change in unemployment (people)", main= "Unemployment");
lines(((nben_h_un_02 - nben_h_un_bs2)*1000), col= "green");
lines(((nben_h_un_03 - nben_h_un_bs3)*1000 ), col= "red");
legend("left", legend=c("Scenario 1","Scenario 2", "Scenario 3"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue", "green", "red"));
grid()
```
